Functional Enrichment Tests: Intro and methods comparison

### 2023-07-10 DRAFT_Funct_Enrich.Rmd
cleaning up annotation derails

```{r}
library(tidyverse)
```

@@

```{r}
blast <- read.csv("DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab", sep = '\t', header = FALSE)
```

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_genomic.fna.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_genomic.fna.gz
```

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_genomic.gff.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_genomic.gff.gz
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("rtracklayer")

# Load the library
library(rtracklayer)

# Define the file path to your GFF file
file_path <- "DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_genomic.gff"

# Import the GFF file
gff_data <- import(file_path)

# Convert GRanges object to a DataFrame for easier manipulation
gff_data_frame <- as.data.frame(gff_data)
```

```{r}
cds <- gff_data_frame %>%
  filter(gbkey == "CDS", source == "Gnomon")
```

>>>>

```{r setup, include=FALSE}
#library(tidyverse)
```

@@

```{r eval=TRUE}}
blast <- read.csv("DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab", sep = '\t', header = FALSE)
```
